Quality Definitions of Qualities

### 2019-11-20 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
updated installability

\begin{defn}
  A measure of the ease of installation.  \wss{Where does this definition come
    from? Please add a citation.  Is it from \citet{McCallEtAl1977}?  I thought
    so originally, but after looking into it, I don't think so anymore.}
\end{defn}

\begin{defn} \label{DefnInstallability}
  Installability is related to the amount of human effort required to install a
  software in a designated environment \citep{berander2005software}.
\end{defn}

@@

\begin{defn}
  ``The efficacy of the installation, uninstallation or reinstallation process
  of a software product in a specified environment'' \citep{iso201017043}
\end{defn}

@@

Definition~\ref{DefnInstallability}.  \wss{This definition does not allow for
  measuring the machine time.}

@@

\wss{The rationale is missing.  Please add.}

>>>>

\begin{defn}
  A measure of the ease of installation \citep{smith2015comparing}.\wss{Where does this definition come
    from? Please add a citation.  Is it from \citet{McCallEtAl1977}?  I thought
    so originally, but after looking into it, I don't think so anymore.}
   \oo{@smith you added the definition in here but I guess it's from here}
\end{defn}

\begin{defn}
  Installability is related to the amount of human effort required to install a
  software in a designated environment \citep{berander2005software}.
\end{defn}

@@

\begin{defn} \label{InstallabilityDefnSelected1}
  ``The efficacy of the installation, uninstallation or reinstallation process
  of a software product in a specified environment'' \citep{iso201017043}
\end{defn}

\begin{defn}
 The degree of effectiveness and efficiency with which a product or system can be successfully installed and/or uninstalled in a specified environment \citep{ISO/IEC25010}.
\end{defn}

\begin{defn} \label{InstallabilityDefnSelected2}
	 Installability refers to the cost or effort required for the installation of a software or product, given an installation is possible to begin with \citep{lenhard2013measuring}
\end{defn}

@@

Definition~ Combined definitions \ref{InstallabilityDefnSelected1} and \ref{InstallabilityDefnSelected2} rephrased.
Installability refers to the cost or effort required for the installation, uninstallation or reinstallation of a software or product in a specified enviroment.  \wss{This definition does not allow for
  measuring the machine time.}

@@

\wss{The rationale is missing.  Please add.}
\oo{The definition allows to measure the cost both from system and human view points}
